\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage[margin=1.2in]{geometry}

\begin{document}

\title{Introduction to EZCAD}
\author{Joseph Zhu}

%\maketitle

%\section{\textit{Launch}}
\section{Launch}
In Windows, create a shortcut.
In Linux, set an alias command.

\section{Create a new project}
Start EZCAD. Select \textsf{Create a new project}, provide \textsf{Project name},
select \textsf{Project path}, click \textsf{Next}.
\textsf{Select modules}, click \textsf{OK}.

%\textbf{Test} % bold face
%\textit{Test} % italic
%\textsc{Test} % small caps
%\textsf{Test} % sans serif
%\textsl{Test} % slanted
%\texttt{Test} % typewriter text

\section{Load survey}
Click \textsf{File}, \textsf{Import}, \textsf{Survey}, \textsf{Tova.db file}.
Select \textsf{tova file}, give \textsf{Survey name}, click \textsf{OK}.

In \textsf{Data explorer}, check \textsf{SURVEY\_BOX\_LABEL} and
 \textsf{SURVEY\_BOX\_LINE}, to turn them on in the viewer.

In the 3D viewer , click the "eye" icon to view all.
Make sure the survey look right.

\section{Load line}

Click \textsf{File}, \textsf{Import}, \textsf{Line}, \textsf{Gocad PLine file
(.pl)}. Select file, give \textsf{Object name}, click \textsf{OK}.

In \textsf{Data explorer}, check the line object to turn it on. Right click
the object, \textsf{Style Editor}, put atom size to 0 for cultural lines.

\section{Load label}

Click \textsf{File}, \textsf{Import}, \textsf{Label}, \textsf{CSV file}.
Select file, give \textsf{Object name}, click \textsf{OK}.

\section{Save project}

Click \textsf{File}, \textsf{Save project}. Look at the \textsf{Process log}.

Click \textsf{File}, \textsf{Quit}. Select \textsf{Yes} at prompt \textsf{
Do you really want to exit?}

\section{Open an old project}

Start EZCAD. Select \textsf{Open an existing project}, select project, click \textsf{Next}.

\section{Save and load object}

Click \textsf{File}, \textsf{Save object}, select object, give filename,
click \textsf{OK}.

Click \textsf{File}, \textsf{Load object}, select file, click \textsf{OK}.

\end{document} 